Titeln på avhandlingens språk

### 2022-12-04 conclusion.tex
Satya & Bobby comments

The study and benchmarking of \ac{WCA} applications is a challenging discipline due to these application's intrinsic human-in-the-loop nature.
Humans are notoriously unreliable, and greatly complicate the scalability and repeatability of experiments.
Furthermore, recruiting large enough cohorts of humans for large-scale experimentation is both greatly time-consuming and prohibitively expensive for many research groups.

In the first half of this paper, we have introduced the \edgedroid{} model of human timing behavior for \ac{WCA}, the first data-driven model for human timings in \ac{WCA} applications.
This model represents a stochastic approach to execution time modeling which builds upon the data collected for \textcite{olguinmunoz:impact2021}.
Together with this model, we have also introduced a novel procedure for the generation of synthetic traces of frames in step-based \ac{WCA}, allowing for a full end-to-end emulation of a human when combined with the timing model.

Next, we have explored the impact of such a realistic model on the application lifetime footprint of \ac{WCA} applications.
We have shown that less realistic modeling approaches which do not take into account higher-order effects on execution time distributions can potentially lead to significant misestimations of application footprint.

Finally, we have delved into the potential for optimization in \ac{WCA} systems using the previously discussed timing models.
We have proposed a novel stochastic optimization framework for resource consumption-system responsiveness trade-offs in \ac{WCA} which results in an adaptive sampling strategy. 
We have shown that this framework is applicable to a myriad of metrics in these applications, and showcased experimental results employing this framework for the minimization of number of samples processed per step and total energy consumption per step.
Our results show up to a \SI{50}{\percent} increase in performance with respect to state of the art when optimizing for number of samples, and up to a \SI{30}{\percent} improvement when optimizing for energy consumption, proving thus the value of such frameworks for the design of \ac{WCA} applications.

This work serves as an important, but yet initial step towards realistic modeling of human behavior in \ac{WCA}, and more generally \ac{AR}.
Many directions remain open to additional exploration in this space.
For instance, our current model only targets a particular class of step-based \ac{WCA}, and extension of our methodology to other classes of these applications, or even more generally to \ac{AR} and \ac{XR}, is on our roadmap.
Our data~\cite{olguinmunoz:impact2021} also only considers young undergraduate students at a highly competitive university in the US.\@
An extension of this dataset and the model towards a more representative sample of the general population would surely be a valuable endeavor.

In terms of the optimization framework, our current approach builds upon the assumption that execution times are Rayleigh-distributed.
Although this distribution fits the data well, there are other which more accurately describe the behavior of human execution times (e.g.\ the \acl{exGaussian}).
Our future efforts consider developing this framework towards these more accurate distributions.
Finally, our current approach only considers a single client, which will be far from the case in a real-world \ac{WCA} deployment.
As such, another milestone in this context could be the exploration for a potential extension towards a collaborative and/or distributed solution.

>>>>

This paper addresses the difficulty of benchmarking \ac{WCA} by offering a model-based alternative to the extensive human-user studies that would otherwise be required.
It first introduces the \edgedroid{} model of human timing behavior for \ac{WCA}, the first data-driven model for human timing in \ac{WCA} applications.
This model represents a stochastic approach to execution time modeling which builds upon prior data~\cite{olguinmunoz:impact2021}.
It further introduces a novel procedure for the generation of synthetic traces of frames in step-based \ac{WCA}, allowing for a full end-to-end emulation of a human when combined with the timing model.

The paper then explores the impact of such a realistic model on the application lifetime footprint of \ac{WCA} applications.
It shows that less realistic modeling approachesm which do not take into account higher-order effects on execution time distributions, can potentially lead to substantial mis-estimations of the application footprint.

Finally, the paper delves into the potential for optimization in \ac{WCA} systems using the previously discussed timing models.
It proposes a novel stochastic optimization framework for resource consumption-system responsiveness trade-offs in \ac{WCA}, which results in an adaptive sampling strategy. 
We have shown that this framework is applicable to a myriad of metrics in these applications, and showcased experimental results employing this framework for the minimization of number of samples processed per step and total energy consumption per step.
Our results show up to a \SI{50}{\percent} increase in performance with respect to state of the art when optimizing for number of samples, and up to a \SI{30}{\percent} improvement when optimizing for energy consumption, thus proving the value of such frameworks for the design of \ac{WCA} applications.

This work serves as an important, yet initial step towards realistic modeling of human behavior in \ac{WCA}, and more generally \ac{AR}.
Many directions remain open to additional exploration in this space.
For instance, our current model only targets a particular class of step-based \ac{WCA}, and extension of our methodology to other classes of these applications, or even more generally to \ac{AR} and \ac{XR}, is on our roadmap.
Our data~\cite{olguinmunoz:impact2021} also only considers young undergraduate students at a highly competitive university in the United States.
An extension of this dataset and the model towards a more representative sample of the general population would surely be a valuable endeavor.
Corresponding research is needed to determine individual difference factors that would substantially impact response to \ac{WCA} in novel populations.

In terms of the optimization framework, our current model adopts the assumption that execution times are Rayleigh-distributed.
Although this distribution fits the data reasonably well, there are other which more accurately describe the behavior of human execution times (e.g.\ the \acl{exGaussian}).
Our future efforts consider developing this framework towards these more accurate distributions.
Finally, our current approach only considers a single client, which will be far from the case in a real-world \ac{WCA} deployment.
As such, another milestone in this context could be the exploration for a potential extension towards a collaborative and/or distributed solution.

\todo[inline]{Comment from Bobby: Reviewers might wonder why we stuck with the Rayleigh distribution.}

### 2022-12-04 implications_footprint.tex
Satya & Bobby comments

In order to illustrate the consequences of using a less realistic model which does not take into account higher order effects, we introduce here a reference model to which we will compare our more realistic models.
This model represents a first-order approximation to empirical execution time modeling, and consist simply of an \ac{exGaussian} distribution fitted to all execution time samples collected for \textcite{olguinmunoz:impact2021}.
This distribution is then randomly sampled at runtime to obtain execution times for each step, without any adjustment to the current state of the system.

>>>>

In order to illustrate the consequences of using a less realistic model that does not take into account higher order effects, we introduce here a reference model to which we will compare our more realistic models.
This model represents a first-order approximation to empirical execution time modeling, and consist simply of an \ac{exGaussian} distribution fitted to all execution time samples collected for \textcite{olguinmunoz:impact2021}.
This distribution is then randomly sampled at runtime to obtain execution times for each step, without any adjustment to the current state of the system.

### 2022-12-04 implications_optimization.tex
Satya & Bobby comments

The results of this investigation are presented in \cref{fig:optimization:samples}, and clearly show the advantages of using the sample-count-optimized scheme over the current state-of-the-art.
The performance of \textcite{Wang2019Towards}'s approach appears to degrade with lower \acp{RTT}, exponentially oversampling as latency tends to zero and the maximum sampling rate of the system tends to infinity.
On the other hand our sampling scheme consistently matches or beats the state-of-the-art while maintaining a relatively constant behavior with respect to \acp{RTT}.
This makes the sample-count-optimized approach more predictable, reliable, and consistent, and thus more suitable for real-world deployments.

It should be noted that although both schemes seem to tend towards \num{2.0} samples per step as \acp{RTT} increase, this is simply an artifact of our experimental setup.
As \acp{RTT} increase way above the expected wait time, the probability of the sum of the first sampling interval and the \ac{RTT} being larger than the execution time of the step tends towards \num{1.0}.
This leads to these sampling schemes consistently sampling only twice each step: a first sample which is taken before the execution time of the step, and a second one \ac{RTT} seconds later, after the execution time has been reached.

>>>>

The results of this investigation are presented in \cref{fig:optimization:samples}, and clearly show the advantages of using the sample-count-optimized scheme over the current state-of-the-art.
The performance of \textcite{Wang2019Towards}'s approach appears to degrade with lower \acp{RTT}, exponentially oversampling as latency tends to zero and the maximum sampling rate of the system tends to infinity.
On the other hand our sampling scheme consistently matches or beats the state-of-the-art while maintaining a relatively constant behavior with respect to \acp{RTT}.
As mentioned above, the future feasibility and mass adoption of \ac{WCA} depends on these applications not hogging the available resources.
Our work advances this goal by being consistently more efficient than existing alternatives at minimizing the number of samples per step, and thus reducing network and processing load.

It should be noted that although both schemes seem to tend towards \num{2.0} samples per step as \acp{RTT} increase, this is simply an artifact of our experimental setup.
As \acp{RTT} increase above the expected wait time, the probability of the sum of the first sampling interval and the \ac{RTT} being larger than the execution time of the step tends towards \num{1.0}.
This leads to these sampling schemes consistently sampling only twice each step: a first sample which is taken before the execution time of the step, and a second one \ac{RTT} seconds later, after the execution time has been reached.

### 2022-12-04 intro.tex
Satya & Bobby comments

A defining characteristic of these applications is their lack of reliance on intentional user inputs to trigger responses.
They are intended to operate as autonomous guides, much akin to how \ac{GPS} systems guide drivers, tracking their progress and providing feedback and instructions at appropriate times.
This context-sensitivity and proactivity in providing user feedback translates into a reliance on high-dimensional, complex, unstructured inputs, such as real-time video feeds, which require intensive compute capabilities to process.
This also translates into latency-sensitivity, as with any \ac{AR} application.
Delays and jitter can be jarring to the user, causing them discomfort, leading to make mistakes and potentially even to abandonment of the application altogether.
On the other hand, as their name suggests, these systems are by design \emph{wearable}, which implies the use of lightweight, battery-powered, low energy consumption devices.

The combination of these opposing characteristic has led to \ac{WCA} applications being identified in research literature as prime candidates for offloading to the edge~\cite{Ha2014towards,Chen2017Empirical,Chen2018application}.
However, many unknowns still remain before consumer-scale adoption of these applications can become a reality.
One key gap in knowledge pertains to the current lack of tools and methodologies for scalable and repeatable study of \ac{WCA} application performance and resource utilization in realistic deployments.
Due to their human-in-the-loop nature, these applications present a challenge to benchmark and characterize, in particular in real-scale deployments where dozens or even hundreds of users might concurrently use the system.
Recruiting a large enough cohort of subjects for realistic benchmarking and study of \ac{WCA} systems can be prohibitively cumbersome and expensive for many research groups and system designers.
Furthermore, humans are unpredictable, and human-subject research is thus often hard to repeat and replicate.
There exists therefore a real need for scalable tools for \ac{WCA} benchmarking which do away with the human-the-loop.

@@

In that context, the contributions of this paper are as follows:
\begin{enumerate}
    \item\label{item:contrib:model} We introduce the first, to our knowledge, data-driven model for human timings in \ac{WCA} applications.
    Using the data collected for \textcite{olguinmunoz:impact2021} as a base, we build a stochastic model which takes as input past measurements of system responsiveness and produces realistic step execution times.
    We also introduce a novel way to generate dynamic traces of frames for \ac{WCA} applications which can be combined with the timing model for a full end-to-end emulation of a human.
    We name this new model \emph{\edgedroid}; a direct, more realistic evolution of our initial EdgeDroid approach~\cite{olguin2018scaling,olguin2019edgedroid}.
    \item\label{item:contrib:footprint} Using the model described above, we study the implications of realistic human behavior on the application lifetime footprint of \ac{WCA}.
    In concordance with previous work~\cite{olguinmunoz:impact2021}, we find dependencies between system responsiveness and human step execution times that lead to substantially different application lifetimes when compared to a first-order baseline which does not take into account human behavior.
    \item\label{item:contrib:optimization} Finally, we study the potential for optimization in \ac{WCA} when considering human behavior using our model.
    We develop a generic model for the stochastic optimization of resource consumption versus responsiveness trade-offs in these applications, which we apply to two potential avenues for \ac{WCA} optimization; number of processed samples and energy consumption per step.
    Compared to the state-of-the-art, our optimization model results in up to \textasciitilde\SI{60}{\percent} fewer samples processed or an average of \SI{20}{\percent} less energy consumed per step, while maintaining comparable levels of responsiveness.
\end{enumerate}

@@

This paper is structured as follows.
\cref{sec:relwork} discusses related work in the field of \acl{WCA} modeling.
In \cref{sec:background} we define and discuss key concepts in \ac{WCA}, as well as summarize the key conclusions from our previous work relating to the relationship between system responsiveness and human behavior in these applications~\cite{olguinmunoz:impact2021}.
In \cref{sec:model} we detail our model for the generation of realistic human timings in \ac{WCA}.
We present its design, verify its expected behavior with respect to our previous results, and introduce the dynamic trace generation for full end-to-end emulation of human behavior.
Next in \cref{sec:implications:footprint} we discuss the potential implications of such a model on application lifetimes by studying a small series of representative scenarios.
This is followed by a more in-depth investigation in \cref{sec:implications:optimization} on the potential consequences of a human timing model on the general optimization of \ac{WCA} systems.
In this section, we also introduce our generic optimization framework for resource consumption versus responsiveness trade-offs in \ac{WCA}.
Finally, in \cref{sec:conclusion} we summarize and conclude this paper, as well as briefly discuss potential avenues for future work.

>>>>

A defining characteristic of these applications is their lack of reliance on intentional user inputs to trigger responses.
They are intended to operate as autonomous guides, much akin to how \ac{GPS} systems guide drivers, tracking their progress and providing feedback and instructions at appropriate times.
This context-sensitivity and proactivity in providing user feedback translates into a reliance on high-dimensional, complex, unstructured inputs, such as real-time video feeds, which require intensive compute capabilities to process.
This also translates into latency-sensitivity, as with any \ac{AR} application.
Delays and jitter can be jarring to the user, causing them discomfort, leading them to make mistakes and potentially even to abandoning the application altogether.
On the other hand, as their name suggests, these systems are by design \emph{wearable}, which implies the use of lightweight, battery-powered, low energy consumption devices.

The combination of these opposing characteristic has led to \ac{WCA} applications being identified in research literature as prime candidates for offloading to the edge~\cite{Ha2014towards,Chen2017Empirical,Chen2018application}.
However, many unknowns still remain before consumer-scale adoption of these applications can become a reality.
One key gap in knowledge pertains to the current lack of tools and methodologies for scalable and repeatable study of \ac{WCA} application performance and resource utilization in realistic deployments.
Due to their human-in-the-loop nature, these applications present a challenge to benchmark and characterize, in particular in real-scale deployments where dozens or even hundreds of users might concurrently use the system.
Accordingly, recruiting a  cohort of subjects for realistic benchmarking and study of \ac{WCA} systems can be prohibitively cumbersome and expensive for many research groups and system designers
There exists therefore a real need for scalable tools for \ac{WCA} benchmarking which do not rely on direct testing of the human-in-the-loop.

@@

In that context, the contributions of this paper are as follows:
\begin{enumerate}
    \item\label{item:contrib:model} We introduce the first, to our knowledge, data-driven model for human timings in \ac{WCA} applications.
    Using the data collected for \textcite{olguinmunoz:impact2021} as a base, we build a stochastic model which takes as input past measurements of system responsiveness and produces realistic step execution times.
    We also introduce a novel way to generate dynamic traces of frames for \ac{WCA} applications which can be combined with the timing model for a full end-to-end emulation of a human.
    We name this new model \emph{\edgedroid}; a direct, more realistic evolution of our initial EdgeDroid approach~\cite{olguin2018scaling,olguin2019edgedroid}.
    \item\label{item:contrib:footprint} Using the model described above, we study the implications of realistic human behavior for the \emph{application lifetime footprint} of \ac{WCA}, understanding this term as the duration of a specific complete execution of the application task.
    In accordance with previous work~\cite{olguinmunoz:impact2021}, we find dependencies between system responsiveness and human step execution times that lead to substantially different application lifetimes when compared to a first-order baseline which does not take into account human behavior.
    \item\label{item:contrib:optimization} Finally, we study the potential for optimization in \ac{WCA} when considering human behavior using our model.
    We develop a generic model for the stochastic optimization of resource consumption versus responsiveness trade-offs in these applications, which we apply to two potential avenues for \ac{WCA} optimization; number of processed samples and energy consumption per step.
    First, we study the potential for reducing the number of samples captured per step.
    This is a valuable endeavor, as reducing the number of samples captured and subsequently processed directly translates in lower bandwidth demand on the wireless network and processor time demand on the cloudlet.
    Next, we explore the potential for direct optimization of energy consumption.
    The economic feasibility of WCA, and hence its likelihood of commercial adoption depends on it not being a resource hog, and this work furthers that effort.
    Compared to the state-of-the-art, our optimization model results in up to \textasciitilde\SI{60}{\percent} fewer samples processed or an average of \SI{20}{\percent} less energy consumed per step, while maintaining comparable levels of responsiveness.
\end{enumerate}

@@

This paper is structured as follows.
\cref{sec:relwork} discusses related work in the field of \acl{WCA} modeling.
In \cref{sec:background} we define and discuss key concepts in \ac{WCA}, as well as summarize the key conclusions from our previous work relating to the relationship between system responsiveness and human behavior in these applications~\cite{olguinmunoz:impact2021}.
In \cref{sec:model} we detail our model for the generation of realistic human timing in \ac{WCA}.
We present its design, verify its expected behavior with respect to our previous results, and introduce the dynamic trace generation for full end-to-end emulation of human behavior.
Next in \cref{sec:implications:footprint} we discuss the potential implications of such a model on application lifetimes by studying a small series of representative scenarios.
This is followed by a more in-depth investigation in \cref{sec:implications:optimization} on the potential consequences of a human timing model on the general optimization of \ac{WCA} systems.
In this section, we also introduce our generic optimization framework for resource consumption versus responsiveness trade-offs in \ac{WCA}.
Finally, in \cref{sec:conclusion} we summarize and conclude this paper, as well as briefly discuss potential avenues for future work.

### 2022-12-04 model.tex
Satya & Bobby comments

In the following, we employ the above insights together with the actual data collected for~\cite{olguinmunoz:impact2021} to design and build a probabilistic model of human behavior for \ac{WCA}.
We detail the construction of a model which uses the data collected to generate, at runtime, realistic execution times. 
In order to accurately emulate the behavior of a human, such a model needs to implement two main behaviors.
One, it needs to generate realistic execution times for each step in the task, considering the current and historical impairment of the \ac{WCA} system.
We detail this in \cref{ssec:model:exectimes}.
And two, it needs to produce sequences of input samples for each step mimicking what a real human would generate; this is explained in \cref{ssec:model:frames}.
% Finally, in \cref{ssec:model:obtaining} we briefly discuss where implementations of this model can be obtained.

>>>>

In the following, we employ the above insights together with the data collected for~\cite{olguinmunoz:impact2021} to design and build a probabilistic model of human behavior for \ac{WCA}.
We detail the construction of a model which uses the data collected to generate, at runtime, realistic execution times. 
In order to accurately emulate the behavior of a human, such a model needs to implement two main behaviors.
First, it needs to generate realistic execution times for each step in the task, considering the current and historical impairment of the \ac{WCA} system, as well as salient individual-difference measures.
We detail this in \cref{ssec:model:exectimes}.
Neuroticism is incorporated in this aspect of the model, as it is the most salient individual difference in the data; however, other factors such as immersive tendency could be treated similarly.
Second, the model must produce sequences of input samples for each step mimicking what a real human would generate; this is explained in \cref{ssec:model:frames}. 
% Finally, in \cref{ssec:model:obtaining} we briefly discuss where implementations of this model can be obtained.

### 2022-12-04 related_work.tex
Satya & Bobby comments

There exist already in literature a number of approaches to the characterization and benchmarking of mobile \ac{XR}, and by extension \ac{WCA}, deployments.
\emph{OpenRTiST}~\cite{george2020openrtist} is a tool which uses a compute-heavy, yet latency-sensitive workload --- image style transfer~\cite{jing2019neural} --- to load and benchmark edge computing deployments.
It acts as an end-to-end realistic \ac{AR} workload, allowing thus researchers to measure the real end-to-end latencies of such systems.
\textcite{Chen2017Empirical} use a number of prototype \ac{WCA} implementation to study and characterize real-world latency bounds in these systems.
In \textcite{lecci2021open}, the authors collect and analyze large amounts of \ac{VR} network traffic, which they then use to construct a synthetic model for the generation of traces of such traffic.
\textcite{chetoui2022arbench} propose \emph{ARBench}, a toolkit for for the benchmarking of mobile hardware in the context of \ac{AR}.
The toolkit incorporates a series of workloads which stress different components of the mobile device and calculates a score for each workload.
\emph{Yahoo Cloud Serving Benchmark}~\cite{cooper2010benchmarking} and \emph{DCBench}~\cite{jia2013characterizing} are workload sets intended for benchmarking cloud services which have further been used in the context of benchmarking edge computing infrastructure for \ac{AR} suitability.
\emph{Edgebench}~\cite{das2018edgebench} and \emph{Defog}~\cite{mcchesney2019defog} benchmark workload performance on the edge versus on the cloud.

@@

The characterization and optimization, of mobile \ac{XR} has also long been a topic of research.
In \textcite{srinivasan2009performance}, the authors analyze a \ac{MAR} workload and identify and characterize the computational bottlenecks in the application.
They proceed to use this characterization to develop a series of code optimizations which allow them to achieve a threefold increase in performance.
The authors of \textcite{Wang2019Towards} develop a taxonomy for \ac{WCA} as well as strategies for workload reduction in these applications, including a novel adaptive sampling scheme with the goal of reducing the number of processed samples while maintaining application responsiveness.
In \textcite{huang2021proactive}, the authors present a framework for the proactive allocation of edge cloud resources while taking into account the inherent mobility of wearable and mobile \ac{AR}.
\textcite{al2017energy} propose an resource allocation strategy which leverages collaboration between \ac{AR} applications to minimize energy consumption.
As above, we have also previously directly contributed to this field.
In \textcite{Moothedath2021EnergyOptimal,Moothedath2022EnergyEfficient} we find the optimum periodic sampling interval which minimizes the energy tracking human progress of a specific subtask in \ac{WCA}.
This is extended into an aperiodic strategy in \textcite{Moothedath2022Aperiodic}.
We further develop this approach in this work by deriving a more practical approximate solution to the aperiodic strategy, which we then use to implement a novel framework for the generic optimization of responsiveness-resource consumption trade-offs.

>>>>

There exist a number of approaches to the characterization and benchmarking of mobile \ac{XR}, and by extension \ac{WCA}, deployments.
\emph{OpenRTiST}~\cite{george2020openrtist} is a tool which uses a compute-heavy, yet latency-sensitive workload --- image style transfer~\cite{jing2019neural} --- to load and benchmark edge computing deployments.
It acts as an end-to-end realistic \ac{AR} workload, allowing thus researchers to measure the real end-to-end latencies of such systems.
\textcite{Chen2017Empirical} use a number of prototype \ac{WCA} implementation to study and characterize real-world latency bounds in these systems.
In \textcite{lecci2021open}, the authors collect and analyze large amounts of \ac{VR} network traffic, which they then use to construct a synthetic model for the generation of traces of such traffic.
\textcite{chetoui2022arbench} propose \emph{ARBench}, a toolkit for for the benchmarking of mobile hardware in the context of \ac{AR}.
The toolkit incorporates a series of workloads which stress different components of the mobile device and calculates a score for each workload.
\emph{Yahoo Cloud Serving Benchmark}~\cite{cooper2010benchmarking} and \emph{DCBench}~\cite{jia2013characterizing} are workload sets intended for benchmarking cloud services which have further been used in the context of benchmarking edge computing infrastructure for \ac{AR} suitability.
\emph{Edgebench}~\cite{das2018edgebench} and \emph{Defog}~\cite{mcchesney2019defog} benchmark workload performance on the edge versus on the cloud.

@@

The characterization and optimization, of mobile \ac{XR} has also long been a topic of research.
In \textcite{srinivasan2009performance}, the authors analyze a \ac{MAR} workload and identify and characterize the computational bottlenecks in the application.
They use this characterization to develop a series of code optimizations which allow them to achieve a threefold increase in performance.
The authors of \textcite{Wang2019Towards} develop a taxonomy for \ac{WCA} as well as strategies for workload reduction in these applications, including a novel adaptive sampling scheme with the goal of reducing the number of processed samples while maintaining application responsiveness.
In \textcite{huang2021proactive}, the authors present a framework for the proactive allocation of edge cloud resources while taking into account the inherent mobility of wearable and mobile \ac{AR}.
\textcite{al2017energy} propose a resource allocation strategy which leverages collaboration between \ac{AR} applications to minimize energy consumption.
As above, we have also previously directly contributed to this field.
In \textcite{Moothedath2021EnergyOptimal,Moothedath2022EnergyEfficient} we find the optimum periodic sampling interval which minimizes the energy tracking human progress of a specific subtask in \ac{WCA}.
This is extended into an aperiodic strategy in \textcite{Moothedath2022Aperiodic}.
We further develop this approach in this work by deriving a more practical approximate solution to the aperiodic strategy, which we then use to implement a novel framework for the generic optimization of responsiveness-resource consumption trade-offs.
